(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2015-04-22 ms/ms.Rnw
Worked on climate variable importance figure

  # Figure of variable importance for latitude
  pdf(paste(pathFig, "/Figure_clim2lat_imp.pdf", sep = ""), 4, 5)
  par(mar = c(5, 6, 1, 1))
  plot(0, 0, type = "n", xlim = c(0, ceiling(vsurfLat$ord.imp$x)[1]), ylim = c(1, 
    length(vsurfLat$varselect.pred)), axes = F, frame.plot = T, xlab = "Importance", 
    ylab = "", cex.lab = 1.5)
  for (i in 1:length(vsurfLat$varselect.pred)) 
  {
     lines(x = c(-1, length(vsurfLat$varselect.pred)), y = c(i, i), col = "grey")
  }
  points(vsurfLat$ord.imp$x[1:length(vsurfLat$varselect.pred)], 
    length(vsurfLat$varselect.pred):1, pch = 21, col = "black", bg = "white", cex = 1.5)
	mtext(climVars[vsurfLat$varselect.pred], side = 2, 
    at = length(vsurfLat$varselect.pred):1, las = 1, line = 1)
	axis(1, lwd = 0, lwd.ticks = 1)
	dev.off()

@@

	plot(0, 0, type = "n", xlim = c(0, 30), ylim = c(1, nImpLat), 
		axes = F, frame.plot = T, xlab = "Importance", ylab = "", cex.lab = 1.5)
	for (i in (nImpLat:(nImpLat - nImpPC1 + 1))) lines(x = c(-100, 100), y = c(i, i), 
		col = "grey")
	points(100 * vsurfPC1$ord.imp$x[1:nImpPC1], nImpLat:(nImpLat - nImpPC1 + 1), pch = 21, 
		col = "black", bg = "white", cex = 1.5)
	mtext(climVars[vsurfPC1$varselect.pred], side = 4, las = 1, line = 1, 
    at = nImpLat:(nImpLat - nImpPC1 + 1), 
		font = ifelse(vsurfPC1$varselect.pred %in% vsurfLat$varselect.pred,	2, 1))
	axis(1, lwd = 0, lwd.ticks = 1, labels = seq(0, 3, 0.5), at = seq(0, 30, 5))
  dev.off()
@

@@

Genotype $\times$ environment interactions are also a common signature of local adaptation [CITE]. For example, populations from more stressful environments may tradeoff reduced growth rate under benign conditions for the ability to tolerate stress by maintaining positive growth rates and/or surviving through adverse conditions. We found remarkably little evidence for this pattern in \textit{M. cardinalis}. There was only one statistically significant Population $\times$ Treatment interaction (Table~\ref{table:Table_AnovaSummary}), but this idiosyncratic result was weak and would not have survived correction for multiple testing. Otherwise, populations responded remarkably similarly to treatments: faster growth in the hot treatment, slower growth in the dry treatment, and high mortality in the hot, dry treatment (Table~\ref{table:Table_AnovaSummary}). Note that interactions were calculated after factoring out intrinsic trait differences, necessarily reducing statistical power to detect significant interactions relative to main effects. However, the fact that the Population and Treatment effects were highly significant ($P \lle 0.001$ in most cases) suggests that statistical power alone cannot explain why we failed to detect Population $\times$ Treatment interactions.

@@

Latitude explains variation
Presumably selective agent is not latitude, but something related to it
Exploratory approach to identify putative selective agent to test in future studies
We used a machine learning approach...identified interannual variation in precipitation
Obviously, cannot identify alternative variables that were not included in analysis.

>>>>

  # Figure of variable importance for latitude
  pdf(paste(pathFig, "/Figure_clim2lat_imp.pdf", sep = ""), 4, 5)
  par(mar = c(5, 6, 1, 1))
  plot(0, 0, type = "n", xlim = c(0, ceiling(vsurfLat$ord.imp$x)[1]), 
		ylim = c(1, length(vsurfLat$varselect.pred)), axes = F, frame.plot = T, 
		xlab = "", ylab = "")
	title(xlab = "Climate-Latitude\nImportance", line = 4, cex.lab = 1.5)
  for (i in 1:length(vsurfLat$varselect.pred)) 
  {
     lines(x = c(-1, length(vsurfLat$varselect.pred)), y = c(i, i), col = "grey")
  }
  points(vsurfLat$ord.imp$x[1:length(vsurfLat$varselect.pred)], 
    length(vsurfLat$varselect.pred):1, pch = 21, col = "black", bg = "white", cex = 1.5)
	# mtext(climVars[vsurfLat$varselect.pred], side = 2, 
    # at = length(vsurfLat$varselect.pred):1, las = 1, line = 1)
	axis(1, lwd = 0, lwd.ticks = 1)
	dev.off()

@@

	plot(0, 0, type = "n", xlim = c(0, 0.3), ylim = c(1, nImpLat), 
		axes = F, frame.plot = T, xlab = "", ylab = "")
	title(xlab = "Climate-Trait PC1\nImportance", line = 4, cex.lab = 1.5)
	for (i in (nImpLat:(nImpLat - nImpPC1 + 1))) 
	{
		lines(x = c(-100, 100), y = c(i, i), col = "grey")
	}
	points(vsurfPC1$ord.imp$x[1:nImpPC1], nImpLat:(nImpLat - nImpPC1 + 1), 
		pch = 21, col = "black", bg = "white", cex = 1.5)
	# mtext(climVars[vsurfPC1$varselect.pred], side = 4, las = 1, line = 1, 
  #  at = nImpLat:(nImpLat - nImpPC1 + 1), 
	#	font = ifelse(vsurfPC1$varselect.pred %in% vsurfLat$varselect.pred,	2, 1))
	axis(1, lwd = 0, lwd.ticks = 1, at = seq(0, 0.3, 0.1))
  dev.off()
@

@@

Genotype $\times$ environment interactions are also a common signature of local adaptation [CITE]. For example, populations from more stressful environments may tradeoff reduced growth rate under benign conditions for the ability to tolerate stress by maintaining positive growth rates and/or surviving through adverse conditions. We found remarkably little evidence for this pattern in \textit{M. cardinalis}. There was only one statistically significant Population $\times$ Treatment interaction (Table~\ref{table:Table_AnovaSummary}), but this idiosyncratic result was weak and would not have survived correction for multiple testing. Otherwise, populations responded remarkably similarly to treatments: faster growth in the hot treatment, slower growth in the dry treatment, and high mortality in the hot, dry treatment (Table~\ref{table:Table_AnovaSummary}). Note that interactions were calculated after factoring out intrinsic trait differences, necessarily reducing statistical power to detect significant interactions relative to main effects. However, the fact that the Population and Treatment effects were highly significant ($P \ll 0.001$ in most cases) suggests that statistical power alone cannot explain why we failed to detect Population $\times$ Treatment interactions.

@@

Latitude explains variation
Presumably selective agent is not latitude, but something related to it
Exploratory approach to identify putative selective agent to test in future studies
We used a machine learning approach...identified interannual variation in precipitation (Fig~\ref{fig:Fig_ClimVarImp})
Obviously, cannot identify alternative variables that were not included in analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure of climatic variable importance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[h!]
	\centerline{\includegraphics[width=1\textwidth]{Figures/Figure_ClimVarImp.pdf}}
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[Interannual variation in precipitation is closely correlated with latitude and trait variation]{CAPTION}
	\label{fig:Fig_ClimVarImp}
\end{figure}

### 2015-04-22 ms/ms.tex
Worked on climate variable importance figure

  \hlcom{# Figure of variable importance for latitude}
  \hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/Figure_clim2lat_imp.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{4}\hlstd{,} \hlnum{5}\hlstd{)}
  \hlkwd{par}\hlstd{(}\hlkwc{mar} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{5}\hlstd{,} \hlnum{6}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{))}
  \hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlkwd{ceiling}\hlstd{(vsurfLat}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x)[}\hlnum{1}\hlstd{]),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,}
    \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)),} \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{xlab} \hlstd{=} \hlstr{"Importance"}\hlstd{,}
    \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
  \hlkwa{for} \hlstd{(i} \hlkwa{in} \hlnum{1}\hlopt{:}\hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred))}
  \hlstd{\{}
     \hlkwd{lines}\hlstd{(}\hlkwc{x} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{1}\hlstd{,} \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)),} \hlkwc{y} \hlstd{=} \hlkwd{c}\hlstd{(i, i),} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
  \hlstd{\}}
  \hlkwd{points}\hlstd{(vsurfLat}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x[}\hlnum{1}\hlopt{:}\hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)],}
    \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)}\hlopt{:}\hlnum{1}\hlstd{,} \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlkwd{mtext}\hlstd{(climVars[vsurfLat}\hlopt{$}\hlstd{varselect.pred],} \hlkwc{side} \hlstd{=} \hlnum{2}\hlstd{,}
    \hlkwc{at} \hlstd{=} \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)}\hlopt{:}\hlnum{1}\hlstd{,} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{1}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in as.graphicsAnnot(text): object 'climVars' not found}}\begin{alltt}
        \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
        \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\begin{alltt}
  \hlcom{# Columns with climatic variables to test}
  \hlkwd{load}\hlstd{(}\hlkwd{paste}\hlstd{(pathDat,} \hlstr{"/Exploratory_climate_variables.RData"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))} \hlcom{#climVars}

  \hlcom{# Variable selection using random forests (VSURF)}
  \hlstd{linmod.PC1} \hlkwb{<-} \hlkwd{as.formula}\hlstd{(}\hlkwd{paste}\hlstd{(}\hlstr{"PC1 ~ "}\hlstd{,} \hlkwd{paste}\hlstd{(climVars,} \hlkwc{collapse} \hlstd{=} \hlstr{" + "}\hlstd{),} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))}
  \hlkwd{set.seed}\hlstd{(}\hlnum{69646}\hlstd{)}
  \hlstd{vsurfPC1} \hlkwb{<-} \hlkwd{VSURF.parallel}\hlstd{(linmod.PC1,} \hlkwc{data} \hlstd{= focClim[,} \hlkwd{c}\hlstd{(}\hlstr{"PC1"}\hlstd{, climVars)],}
    \hlkwc{ncores} \hlstd{=} \hlnum{3}\hlstd{)}
\end{alltt}

@@

        \hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{30}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, nImpLat),}
                \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{xlab} \hlstd{=} \hlstr{"Importance"}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlkwa{for} \hlstd{(i} \hlkwa{in} \hlstd{(nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{)))} \hlkwd{lines}\hlstd{(}\hlkwc{x} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{100}\hlstd{,} \hlnum{100}\hlstd{),} \hlkwc{y} \hlstd{=} \hlkwd{c}\hlstd{(i, i),}
                \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
        \hlkwd{points}\hlstd{(}\hlnum{100} \hlopt{*} \hlstd{vsurfPC1}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x[}\hlnum{1}\hlopt{:}\hlstd{nImpPC1], nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{),} \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,}
                \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlkwd{mtext}\hlstd{(climVars[vsurfPC1}\hlopt{$}\hlstd{varselect.pred],} \hlkwc{side} \hlstd{=} \hlnum{4}\hlstd{,} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{1}\hlstd{,}
    \hlkwc{at} \hlstd{= nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{),}
                \hlkwc{font} \hlstd{=} \hlkwd{ifelse}\hlstd{(vsurfPC1}\hlopt{$}\hlstd{varselect.pred} \hlopt{%in%} \hlstd{vsurfLat}\hlopt{$}\hlstd{varselect.pred,}     \hlnum{2}\hlstd{,} \hlnum{1}\hlstd{))}
        \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{3}\hlstd{,} \hlnum{0.5}\hlstd{),} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{30}\hlstd{,} \hlnum{5}\hlstd{))}
  \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

Genetic differences between populations affecting originsmal function and performance point to traits that may be involved in local adaptation. Using a common garden design, we identified strong genetic differences in germination, growth, and photosynthetic rate among populations of \textit{M. cardinalis} (Table~\ref{Table_AnovaSummary}). A single principal component captured 74.2 %\% of among population trait variation, defining an axis of variation from fast to slow growth (Fig~\ref{Fig_PC1vLat}). As we explain below, intrinsic differences between populations in terms of plant function (photosynthesis) and performance (growth) contrasted greatly with little variation in plasticity.

@@

Genotype by environment interactions are also a common signature of local adaptation [CITE]. For example, populations from more stressful environments may tradeoff reduced growth rate under benign conditions for the ability to tolerate stress by maintaining positive growth rates and/or surviving through adverse conditions. We found remarkably little evidence for this pattern in \textit{M. cardinalis}.

Do not think this is a power issue because statistical signifiance of treatment and populations effects were very high.

@@

>>>>

        \hlcom{# Load climVars}
        \hlkwd{load}\hlstd{(}\hlkwd{paste}\hlstd{(pathDat,} \hlstr{"/ExploratoryCimateVariables.RData"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))}

  \hlcom{# Figure of variable importance for latitude}
  \hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/Figure_clim2lat_imp.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{4}\hlstd{,} \hlnum{5}\hlstd{)}
  \hlkwd{par}\hlstd{(}\hlkwc{mar} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{5}\hlstd{,} \hlnum{6}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{1}\hlstd{))}
  \hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlkwd{ceiling}\hlstd{(vsurfLat}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x)[}\hlnum{1}\hlstd{]),}
                \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)),} \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,}
                \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
        \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Climate-Latitude\textbackslash{}nImportance"}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
  \hlkwa{for} \hlstd{(i} \hlkwa{in} \hlnum{1}\hlopt{:}\hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred))}
  \hlstd{\{}
     \hlkwd{lines}\hlstd{(}\hlkwc{x} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{1}\hlstd{,} \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)),} \hlkwc{y} \hlstd{=} \hlkwd{c}\hlstd{(i, i),} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
  \hlstd{\}}
  \hlkwd{points}\hlstd{(vsurfLat}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x[}\hlnum{1}\hlopt{:}\hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)],}
    \hlkwd{length}\hlstd{(vsurfLat}\hlopt{$}\hlstd{varselect.pred)}\hlopt{:}\hlnum{1}\hlstd{,} \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlcom{# mtext(climVars[vsurfLat$varselect.pred], side = 2, }
    \hlcom{# at = length(vsurfLat$varselect.pred):1, las = 1, line = 1)}
        \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
        \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\begin{alltt}
  \hlcom{# Variable selection using random forests (VSURF)}
  \hlstd{linmod.PC1} \hlkwb{<-} \hlkwd{as.formula}\hlstd{(}\hlkwd{paste}\hlstd{(}\hlstr{"PC1 ~ "}\hlstd{,} \hlkwd{paste}\hlstd{(climVars,} \hlkwc{collapse} \hlstd{=} \hlstr{" + "}\hlstd{),} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))}
  \hlkwd{set.seed}\hlstd{(}\hlnum{69647}\hlstd{)}
  \hlstd{vsurfPC1} \hlkwb{<-} \hlkwd{VSURF.parallel}\hlstd{(linmod.PC1,} \hlkwc{data} \hlstd{= focClim[,} \hlkwd{c}\hlstd{(}\hlstr{"PC1"}\hlstd{, climVars)],}
    \hlkwc{ncores} \hlstd{=} \hlnum{3}\hlstd{)}
\end{alltt}

@@

        \hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.3}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{, nImpLat),}
                \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{xlab} \hlstd{=} \hlstr{""}\hlstd{,} \hlkwc{ylab} \hlstd{=} \hlstr{""}\hlstd{)}
        \hlkwd{title}\hlstd{(}\hlkwc{xlab} \hlstd{=} \hlstr{"Climate-Trait PC1\textbackslash{}nImportance"}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{4}\hlstd{,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlkwa{for} \hlstd{(i} \hlkwa{in} \hlstd{(nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{)))}
        \hlstd{\{}
                \hlkwd{lines}\hlstd{(}\hlkwc{x} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{100}\hlstd{,} \hlnum{100}\hlstd{),} \hlkwc{y} \hlstd{=} \hlkwd{c}\hlstd{(i, i),} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
        \hlstd{\}}
        \hlkwd{points}\hlstd{(vsurfPC1}\hlopt{$}\hlstd{ord.imp}\hlopt{$}\hlstd{x[}\hlnum{1}\hlopt{:}\hlstd{nImpPC1], nImpLat}\hlopt{:}\hlstd{(nImpLat} \hlopt{-} \hlstd{nImpPC1} \hlopt{+} \hlnum{1}\hlstd{),}
                \hlkwc{pch} \hlstd{=} \hlnum{21}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"black"}\hlstd{,} \hlkwc{bg} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
        \hlcom{# mtext(climVars[vsurfPC1$varselect.pred], side = 4, las = 1, line = 1, }
  \hlcom{#  at = nImpLat:(nImpLat - nImpPC1 + 1), }
        \hlcom{#	font = ifelse(vsurfPC1$varselect.pred %in% vsurfLat$varselect.pred,	2, 1))}
        \hlkwd{axis}\hlstd{(}\hlnum{1}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.3}\hlstd{,} \hlnum{0.1}\hlstd{))}
  \hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

Genetic differences between populations affecting originsmal function and performance point to traits that may be involved in local adaptation. Using a common garden design, we identified strong genetic differences in germination, growth, and photosynthetic rate among populations of \textit{M. cardinalis} (Table~\ref{table:Table_AnovaSummary}). A single principal component captured 74.2 %$\%$ of the trait variation among populations, defining an axis of variation from fast to slow growth (Fig~\ref{fig:Fig_PC1vLat}). As we explain below, intrinsic differences between populations in terms of plant function (photosynthesis) and performance (growth) contrasted greatly with little variation in plasticity.

@@

Genotype $\times$ environment interactions are also a common signature of local adaptation [CITE]. For example, populations from more stressful environments may tradeoff reduced growth rate under benign conditions for the ability to tolerate stress by maintaining positive growth rates and/or surviving through adverse conditions. We found remarkably little evidence for this pattern in \textit{M. cardinalis}. There was only one statistically significant Population $\times$ Treatment interaction (Table~\ref{table:Table_AnovaSummary}), but this idiosyncratic result was weak and would not have survived correction for multiple testing. Otherwise, populations responded remarkably similarly to treatments: faster growth in the hot treatment, slower growth in the dry treatment, and high mortality in the hot, dry treatment (Table~\ref{table:Table_AnovaSummary}). Note that interactions were calculated after factoring out intrinsic trait differences, necessarily reducing statistical power to detect significant interactions relative to main effects. However, the fact that the Population and Treatment effects were highly significant ($P \ll 0.001$ in most cases) suggests that statistical power alone cannot explain why we failed to detect Population $\times$ Treatment interactions.

@@

Latitude explains variation
Presumably selective agent is not latitude, but something related to it
Exploratory approach to identify putative selective agent to test in future studies
We used a machine learning approach...identified interannual variation in precipitation (Fig~\ref{fig:Fig_ClimVarImp})
Obviously, cannot identify alternative variables that were not included in analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure of climatic variable importance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[h!]
	\centerline{\includegraphics[width=1\textwidth]{Figures/Figure_ClimVarImp.pdf}}
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[Interannual variation in precipitation is closely correlated with latitude and trait variation]{CAPTION}
	\label{fig:Fig_ClimVarImp}
\end{figure}
